Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
remove fig1
meh
remove junk from paper

\subsection{Selecting optimal feature combination}
\newcommand\ward{backward} %or maybe backwards

We used a \ward stepwise approach to identifying optimal feature combinations.
We first ran the system with all features on, producing a total of $256=2^8$
combinations.  We then used backwards stepwise regression to identify feature
combinations with a small number of features but with high performance

@@

Fortunately, the classifiers were very fast, and almost all of the time the
system spends is in reading input and building feature sets, which don't need
to be repeated, so bootstrapping is very cheap to include.

@@

\section{Methods}
\newcommand\few{few}

We ran the system with several hundred different combinations of features over
all the words in the input set.

@@

We ran a more detailed analysis on the top \few systems.  This analysis included
consideration of all three grain-levels of score and scores by word.

@@

\begin{figure}
\includegraphics[width=\textwidth]{baseline}
\caption{\label{fig:base}Baseline scores for our two baseline systems}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{pg_0001}
\caption{\label{fig1}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{pg_0002}
%stepwise graph 1
%classifiert, collocation, cooccurrence  
%Interpret this graph
\caption{\label{fig2}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{pg_0003}
\caption{\label{fig3}}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}}
\end{figure}

>>>>

@@

Fortunately, the classifiers were very fast, and almost all of the time the
system spends is in reading input and building feature sets, which don't need
to be repeated, so bootstrapping is very cheap to include.  The probability measure that we used for the algorithm was 0.8

@@

\section{Methods}
We ran the system with several hundred different combinations of features over
all the words in the input set.

@@

We ran a more detailed analysis on the top system.  This analysis included
consideration of all three grain-levels of score and scores by word.

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{baseline}
\caption{\label{fig:base}Baseline scores for our two baseline systems}
\end{figure}

@@

%\begin{figure}[H]
%\includegraphics[width=\textwidth]{pg_0001}
%\caption{\label{fig1}}
%\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{pg_0002}
%stepwise graph 1
%classifiert, collocation, cooccurrence  
%Interpret this graph
\caption{\label{fig2}}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{pg_0003}
\caption{\label{fig3}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}}
\end{figure}
